Signed Peripherality Functions for Multivariate Statistical Inference

### 2018-03-30 MS-new/7_Appendix.tex
new draft sent to anshu da

\begin{Corollary} \label{Corollary:eigendist}
Consider the sample DCM $ \tilde \BS = \sum_{i=1}^n (D^{n-}_\bfX (\bfx_i))^2 \BS (\bfx_i; \hat\bfmu_n)/n $ and its spectral decomposition $\tilde \BS = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $. Then the matrices $\BG_D = \sqrt n (\hat\Gamma_D - \Gamma) $ and $\BL_D = \sqrt n (\hat\Lambda_D - \Lambda_{D}) $ have independent distributions. The random variable $\ve(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $\BG_D = (\bfg_1,...,\bfg_p)$ are as follows:
%
\begin{equation} \label{equation:DevEq}
A\BV(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ik}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ]}
{(\lambda_{D,i} - \lambda_{D,k})^2} \bfgamma_k \bfgamma_k^T
\end{equation}
%
\begin{equation}
A\BC( \bfg_i, \bfg_j) = - \frac{\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ij}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ]}
{(\lambda_{D,i} - \lambda_{D,j})^2} \bfgamma_i \bfgamma_j^T; \quad i \neq j
\end{equation}
%
The vector consisting of diagonal elements of $\BL_D$, say $\mathbf{\ell} = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
%
\begin{eqnarray}
A\BV(l_i) &=&\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ii}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ] - \lambda_{D,i}^2,\\
A\BC(l_i, l_j) &=& \BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ij}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ] - \lambda_{D,i} \lambda_{D,j}; \quad i \neq j.
\end{eqnarray}
%
\end{Corollary}

@@

\newpage
\section{Proofs}
\label{section:appC}

@@

\noindent\textbf{(C1)}$\text{Tr}(\Sigma^4) = o(\text{Tr}^2(\Sigma^2)) $,

\noindent\textbf{(C2)}$\text{Tr}^4(\Sigma) / \text{Tr}^2(\Sigma^2) \exp[ - \text{Tr}^2(\Sigma) / 128p \lambda^2_{\max}(\Sigma) ] = o(1)$
\vspace{1em}

\noindent when $H_0$ is true we have
%
\begin{eqnarray}
E[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^4 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^2 ]\\
E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]\\
E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w2})^2 ] &=& o(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]
\end{eqnarray}
%
with $\bfepsilon \sim \mathcal E({\bf 0}_p, \Lambda, G)$ and $\bfepsilon_w = w(\bfepsilon) \bfS(\bfepsilon)$.
\end{Lemma}
%
A proof of this lemma is derived using results in section 3 of \cite{ElKaroui09}, noticing that any-scalar valued 1-Lipschitz function of $\bfepsilon_w$ is a $M_w$-Lipschitz function of $\bfS(\bfepsilon)$, with $M_w = \sup_\bfepsilon w(\bfepsilon)$. Same steps as in the proof of Theorem 2.2 in \cite{WangPengLi15} follow now, using the lemma above in place of Lemma 2.1 therein, to establish asymptotic normality of $C_{n,w}$ under $H_0$.

@@

\begin{Lemma}
Given that condition (C3) holds, we have $\lambda_{\max} (B_w) \leq 2 \frac{\lambda_{\max}}{\text{Tr} (\Sigma)} (1+o(1))$.
\end{Lemma}

\begin{Lemma}
Define $D_w = E \left[ \frac{w^2(\bfepsilon)}{\| \bfepsilon \|^2} (I_p - \bfS(\bfepsilon) \bfS(\bfepsilon)^T )\right] $. Then $\lambda_{\max} (A_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)$ and $\lambda_{\max} (D_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)^2$. Further, if (C3) and (C4) hold then $\lambda_{\min} (A_w) \geq E( w(\bfepsilon)/\| \bfepsilon \|)(1+o(1))/\sqrt 3$.
\end{Lemma}
%
The proof now exactly follows steps in the proof of theorem 2.3 in \cite{WangPengLi15}, replacing vector signs by weighted signs, using the fact that $w(\bfepsilon)$ is bounded above by $M_w$ while applying conditions (C5)-(C6) and lemmas A.1, A.2, A.3, and finally using the above two lemmas in place of lemmas A.4 and A.5 respectively.
\end{proof}

\begin{proof}[Proof of Theorem  \ref{Theorem:covform}]
The proof follows directly from writing out the expression of $Cov ( \tilde \bfX)$:
%
\begin{eqnarray*}
Cov(\tilde\bfX) &=& E(\tilde\bfX \tilde\bfX^T) - E(\tilde\bfX) E(\tilde\bfX)^T\\
&=& \Gamma . E \left[ (D^-_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
&=& \Gamma .E \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
\end{eqnarray*}
%
\end{proof}

\begin{proof}[Proof of Lemma \ref{Lemma:lemma1}]
For two positive definite matrices $A,B$, we denote by $A>B$ that $A-B$ is positive definite. Also, denote
%
$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
%
%Consider now the quantity $\bft^T S_n \bft$, where $\bft \in \mathbb{R}^p$. Now applying Cauchy-Schwarz inequality we shall have
%%
%\begin{eqnarray}\label{eqn:AppEqn1}
%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
%\end{eqnarray}
%%
%with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
Now due to the assumption of uniform convergence, given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
%
\begin{equation}
\label{equation:lemma1eq}
| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (D^-_\bfX(\bfx_i))^2 | < \epsilon
\end{equation}
%
for all $n_1 \geq N; i = 1,2,...,n_1$. This implies
%
\begin{eqnarray}
\label{eqn:lemma1eq2}
S_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ SS(\bfx_i; \hat\bfmu_{n_1}) - SS(\bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \bfmu) \right]
\end{eqnarray}

We now construct a sequence of positive definite matrices $\{A_k (B_k+C_k) : k \in \mathbb N\} $ so that
%
$$ A_k = \frac{1}{k}, \quad B_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right]$$
$$\quad C_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
%
where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$. Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $B_k = o_P(1)$, thus $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.

Now (\ref{eqn:lemma1eq2}) implies that for any $\epsilon_1 > 0$, $S_{N_k} > \epsilon_1 \Rightarrow A_k (B_k + C_k) > \epsilon_1$, which means $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$. Hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$. Since the main sequence $\{S_k\}$ is bounded below by 0, this implies $\{S_k\} \stackrel{P}{\rightarrow} 0$. Finally, we have that
%
\begin{eqnarray}
\sqrt n \left[
\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
\frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
\end{eqnarray}
%
Since the second summand on the right hand side is $o_P(1)$ due to \cite{durre14} as mentioned before, we have the needed.
\end{proof}

\begin{proof}[Proof of Theorem \ref{Theorem:rootn}]
The quantity in the statement of the theorem can be broken down as:
%
\begin{eqnarray*}
\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (D^-_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
\end{eqnarray*}
%
The first part goes to 0 in probability by Lemma \ref{Lemma:lemma1}, and applying Slutsky's theorem we get the required convergence.
\end{proof}

@@

\item $\| \hat\Lambda - \Lambda \|_F \stackrel{P}{\rightarrow} 0$
\end{enumerate}
%
as $n \rightarrow \infty$. For (1), we notice $\sqrt n vec(\hat\Gamma_D - \Gamma)$ asymptotically has a (singular) multivariate normal distribution following Corollary \ref{Corollary:eigendist}, so that $\| \hat\Gamma_D - \Gamma \|_F = O_P(1/\sqrt n)$ using Prokhorov's theorem.

It is now enough to prove convergence in probability of the individual eigenvalue estimates $\hat\lambda_i; i = 1,...,p$. For this, define estimates $\tilde\lambda_i$ as median-of-small-variances estimator of the \textit{true} score vectors $\Gamma^T X$. For this we have
%
\begin{equation}\label{eqn:PluginSigmaProof1}
| \tilde\lambda_i - \lambda_i | \stackrel{P}{\rightarrow} 0
\end{equation}
%
using Theorem 3.1 of \cite{Minsker15}, with $\mu = \lambda_i$. Now $ \hat\lambda_i = \text{med}_j (Var( X_{G_j}^T \hat\bfgamma_{D,i} ))$ and $\tilde\lambda_i = \text{med}_j (Var( X_{G_j}^T \bfgamma_i )) $, so that
%
\begin{eqnarray*}
| \hat\lambda_i - \tilde\lambda_i | &\leq & \text{med}_j \left[ Var( X_{G_j}^T ( \hat\bfgamma_{D,i} - \bfgamma_i) ) \right]
\\ &\leq & \| \hat\bfgamma_{D,i} - \bfgamma_i \|^2 \text{med}_j  \left[ \text{Tr} (Cov ( X_{G_j})) \right]
\end{eqnarray*}
%
using Cauchy-Schwarz inequality. Combining the facts $ \| \hat\bfgamma_{D,i} - \bfgamma_i \| = O_P(1/\sqrt n)$ and $ \text{med}_j  [ \text{Tr} (Cov ( X_{G_j})) ] \stackrel{P}{\rightarrow} \text{Tr}(\Sigma)$ \citep{Minsker15} with (\ref{eqn:PluginSigmaProof1}), we get the needed.

@@

\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}. Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:

$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$

So that for eigenvector estimates of the original $F$ we have

\begin{equation} \label{equation:app1}
\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
\end{equation}

$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies

$$ A\BV(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$

For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,

\begin{eqnarray*}
ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
&=& - \frac{A\BV(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
\end{eqnarray*}

>>>>

\begin{Corollary} \label{Corollary:eigendist}
Consider the sample DCM $ \tilde \BS = \sum_{i=1}^n (D^{n-}_\bfX (\bfx_i))^2 \BS (\bfx_i; \hat\bfmu_n)/n $ and its spectral decomposition $\tilde \BS = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $. Then the matrices $\BG_D = \sqrt n (\hat\Gamma_D - \Gamma) $ and $\BL_D = \sqrt n (\hat\Lambda_D - \Lambda_{D}) $ have independent distributions. The random variable $\ve(\BG_D)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $\BG_D = (\bfg_1,...,\bfg_p)$ are as follows:
%
\begin{equation} \label{equation:DevEq}
A\BV(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ik}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ]}
{(\lambda_{D,i} - \lambda_{D,k})^2} \bfgamma_k \bfgamma_k^T
\end{equation}
%
\begin{equation}
A\BC( \bfg_i, \bfg_j) = - \frac{\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ij}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ]}
{(\lambda_{D,i} - \lambda_{D,j})^2} \bfgamma_i \bfgamma_j^T; \quad i \neq j
\end{equation}
%
The vector consisting of diagonal elements of $\BL_D$, say $\mathbf{\ell} = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
%
\begin{eqnarray}
A\BV(l_i) &=&\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ii}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ] - \lambda_{D,i}^2,\\
A\BC(l_i, l_j) &=& \BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ij}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ] - \lambda_{D,i} \lambda_{D,j}; \quad i \neq j.
\end{eqnarray}
%
\end{Corollary}

@@

\section{Proofs}
\label{section:appC}

@@

\noindent\textbf{(C1)}$\Tr(\Sigma^4) = o(\Tr^2(\Sigma^2)) $,

\noindent\textbf{(C2)}$\Tr^4(\Sigma) / \Tr^2(\Sigma^2) \exp[ - \Tr^2(\Sigma) / 128p \lambda^2_{\max}(\Sigma) ] = o(1)$
\vspace{1em}

\noindent when $H_0$ is true we have
%
\begin{eqnarray}
\BE[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^4 ] &=& O(1) \BE^2[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^2 ],\\
\BE[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ] &=& O(1) \BE^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ],\\
\BE[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w2})^2 ] &=& o(1) \BE^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ],
\end{eqnarray}
%
with $\bfepsilon \sim \mathcal E({\bf 0}_p, \Lambda, g)$ and $\bfepsilon_w = w(\bfepsilon) \bfS(\bfepsilon)$.
\end{Lemma}
%
A proof of this lemma is derived using results in section 3 of \cite{ElKaroui09}, noticing that any-scalar valued 1-Lipschitz function of $\bfepsilon_w$ is a $M_w$-Lipschitz function of $\bfS(\bfepsilon)$, with $M_w = \sup_\bfepsilon w(\bfepsilon)$. Same steps as in the proof of Theorem 2.2 in \cite{WangPengLi15} follow now, using the lemma above in place of Lemma 2.1 therein, to establish asymptotic normality of $C_{n,w}$ under $H_0$.

@@

\begin{Lemma}
Given that condition (C3) holds, we have $\lambda_{\max} (\BB_w) \leq 2 \frac{\lambda_{\max}}{\text{Tr} (\Sigma)} (1+o(1))$.
\end{Lemma}

\begin{Lemma}
Define $\BD_w = \BE \left[ \frac{w^2(\bfepsilon)}{\| \bfepsilon \|^2} (\BI_p - \bfS(\bfepsilon) \bfS(\bfepsilon)^T )\right] $. Then $\lambda_{\max} (\BA_w) \leq \BE( w(\bfepsilon)/\| \bfepsilon \|)$ and $\lambda_{\max} (\BD_w) \leq \BE( w(\bfepsilon)/\| \bfepsilon \|)^2$. Further, if (C3) and (C4) hold then $\lambda_{\min} (\BA_w) \geq \BE( w(\bfepsilon)/\| \bfepsilon \|)(1+o(1))/\sqrt 3$.
\end{Lemma}
%
The proof now exactly follows steps in the proof of theorem 2.3 in \cite{WangPengLi15}, replacing vector signs by weighted signs, using the fact that $w(\bfepsilon)$ is bounded above by $M_w$ while applying conditions (C5)-(C6) and lemmas A.1, A.2, A.3, and finally using the above two lemmas in place of lemmas A.4 and A.5 respectively.
\end{proof}

\begin{proof}[Proof of Theorem  \ref{Theorem:covform}]
The proof follows directly from writing out the expression of $Cov ( \tilde \bfX)$:
%
\begin{eqnarray*}
\BV \tilde\bfX &=& \BE (\tilde\bfX \tilde\bfX^T) - \BE \tilde\bfX \BE \tilde\bfX^T\\
&=& \Gamma . \BE \left[ (D^-_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
&=& \Gamma . \BE \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
\end{eqnarray*}
%
\end{proof}

\begin{proof}[Proof of Lemma \ref{Lemma:lemma1}]
For two positive definite matrices $\BA, \BB$, we denote by $ \BA > \BB$ that $\BA-\BB$ is positive definite. Also, denote
%
$$
\BS_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| ( D^{n-} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right| \BS( \bfx_i; \hat\bfmu_n) \right].
$$
%
%Consider now the quantity $\bft^T S_n \bft$, where $\bft \in \mathbb{R}^p$. Now applying Cauchy-Schwarz inequality we shall have
%%
%\begin{eqnarray}\label{eqn:AppEqn1}
%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
%\end{eqnarray}
%%
%with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
Due to assumption (D1), given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
%
\begin{equation}
\label{equation:lemma1eq}
| (D^{n_1 -}_\bfX(\bfx_i))^2 - (D^-_\bfX(\bfx_i))^2 | < \epsilon
\end{equation}
%
for all $n_1 \geq N; i = 1,2,...,n_1$. This implies
%
\begin{eqnarray}
\BS_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \BS( \bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ \BS( \bfx_i; \hat\bfmu_{n_1}) - \BS( \bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} \BS( \bfx_i; \bfmu) \right]\label{eqn:lemma1eq2}
\end{eqnarray}

We now construct a sequence of positive definite matrices $\{a_k (B_k+C_k) : k \in \mathbb N\} $ so that
%
$$
a_k = \frac{1}{k}, \quad \BB_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ \BS( \bfx_i; \hat\bfmu_{N_k}) - \BS(\bfx_i; \bfmu) \right\} \right],
\quad \BC_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \BS(\bfx_i; \bfmu) \right]
$$
%
where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$. Under conditions $ \BE \|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $\BB_k = o_P(1)$, thus $a_k (\BB_k + \BC_k) \stackrel{P}{\rightarrow} 0$.

Now \eqref{eqn:lemma1eq2} implies that for any $\epsilon_1 > 0$, $\BS_{N_k} > \epsilon_1 \Rightarrow a_k (\BB_k + \BC_k) > \epsilon_1$, which means $ P(\BS_{N_k} > \epsilon_1) < P(a_k (\BB_k + \BC_k) > \epsilon_1)$. Hence the subsequence $\{\BS_{N_k}\} \stackrel{P}{\rightarrow} 0$. Since the main sequence $\{\BS_k\}$ is bounded below by 0, this implies $\{\BS_k\} \stackrel{P}{\rightarrow} 0$. Finally, we have that
%
\begin{eqnarray}
\sqrt n \left[
\frac{1}{n} \sum_{i=1}^n ( D^{n-}_\bfX (\bfx_i))^2 \BS(\bfx_i; \hat\bfmu_n) -
\frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 \BS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
\BS_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ \BS(\bfx_i; \hat\bfmu_{n}) - \BS(\bfx_i; \bfmu) \right\} \right] &&
\end{eqnarray}
%
Since the second summand on the right hand side is $o_P(1)$ due to \cite{durre14} as mentioned before, we have the needed.
\end{proof}

\begin{proof}[Proof of Theorem \ref{Theorem:rootn}]
The quantity in the statement of the theorem can be broken down as:
%
\begin{eqnarray*}
\sqrt n \left[ \ve \left\{ \frac{1}{n} \sum_{i=1}^n ( D^{n-}_\bfX (\bfx_i))^2 \BS(\bfx_i; \hat\bfmu_n) \right\} - \ve \left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 \BS( \bfx_i; \bfmu) \right\} \right] +\\
\sqrt n \left[ \ve \left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 \BS( \bfx_i; \bfmu) \right\} - \BE \left[ \ve \left\{ (D^-_\bfX (\bfx))^2 \BS( \bfx; \bfmu) \right\} \right] \right]
\end{eqnarray*}
%
The first part goes to 0 in probability by Lemma \ref{Lemma:lemma1}, and applying Slutsky's theorem we get the required convergence.
\end{proof}

@@

\item $\| \hat\Lambda - \Lambda \|_F \stackrel{P}{\rightarrow} 0$,
\end{enumerate}
%
as $n \rightarrow \infty$. For (1), we notice $\sqrt n \ve ( \hat\Gamma_D - \Gamma)$ asymptotically has a (singular) multivariate normal distribution following Corollary \ref{Corollary:eigendist}, so that $\| \hat\Gamma_D - \Gamma \|_F = O_P(1/\sqrt n)$ using Prokhorov's theorem.

It is now enough to prove convergence in probability of the individual eigenvalue estimates $\hat\lambda_i; i = 1,...,p$. For this, define estimates $\tilde\lambda_i$ as median-of-small-variances estimator of the \textit{true} score vectors $\Gamma^T \bfX$. For this we have
%
\begin{equation}\label{eqn:PluginSigmaProof1}
| \tilde\lambda_i - \lambda_i | \stackrel{P}{\rightarrow} 0
\end{equation}
%
using Theorem 3.1 of \cite{Minsker15}, with $\mu = \lambda_i$. Now $ \hat\lambda_i = \text{median}_j ( \BS ( \BX_{G_j} \hat\bfgamma_{D,i} ))$ and $\tilde\lambda_i = \text{median}_j ( \BS( \BX_{G_j} \bfgamma_i )) $, so that
%
\begin{eqnarray*}
| \hat\lambda_i - \tilde\lambda_i | &\leq & \text{median}_j \left[ \BS( \BX_{G_j} ( \hat\bfgamma_{D,i} - \bfgamma_i) ) \right]
\\ &\leq & \| \hat\bfgamma_{D,i} - \bfgamma_i \|^2 \text{median}_j  \left[ \text{Tr} ( \BS( \BX_{G_j}) ) \right]
\end{eqnarray*}
%
using Cauchy-Schwarz inequality. Combining the facts $ \| \hat\bfgamma_{D,i} - \bfgamma_i \| = O_P(1/\sqrt n)$ and $ \text{median}_j  [ \text{Tr} (\BS ( X_{G_j})) ] \stackrel{P}{\rightarrow} \text{Tr}(\Sigma)$ \citep{Minsker15} with (\ref{eqn:PluginSigmaProof1}), we get the needed.

@@

\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}. Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\tilde \BS (\BF_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (\BF_\Lambda)$:

$$ \sqrt n \hat\gamma_{D,ij} (\BF_\Lambda) = \sqrt n \frac{\tilde \BS_{ij} (\BF_\Lambda)}{\lambda_{D,i} - \lambda_{D,j}}; \quad i \neq j$$

So that for eigenvector estimates of the original $F$ we have
%
\begin{align}
\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) &= \sqrt n \Gamma (\hat \bfgamma_{D,i}(\BF_\Lambda) - \bfe_i )\notag\\
&= \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(\BF_\Lambda )\bfgamma_k + (\hat \gamma_{D,ii}(\BF_\Lambda) - 1)\bfgamma_i \right].\label{equation:app1}
\end{align}

By assumption we now have $\sqrt n (\hat \gamma_{D,ii}(\BF_\Lambda) - 1) =  o_P(1)$ and $A\BV( \sqrt n \tilde \BS_{ik}(\BF_\Lambda), \sqrt n \tilde \BS_{il}(\BF_\Lambda)) = 0$ for $k \neq l$, so the above equation implies
%
$$
A\BV(\bfg_i) = A\BV (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) =
\sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \tilde \BS_{ik}(\BF_\Lambda))}{(\lambda_{D,i} - \lambda_{D,k})^2} \bfgamma_k \bfgamma_k^T
$$

For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,
%
\begin{eqnarray*}
A\BV( \bfg_i, \bfg_j) &=& A\BV (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
&=& A\BV \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(\BF_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(\BF_\Lambda)\bfgamma_k \right)\\
&=& A\BV \left( \sqrt n \hat \gamma_{D,ij}(\BF_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(\BF_\Lambda)\bfgamma_i \right)\\
&=& - \frac{A\BV( \sqrt n \tilde \BS_{ij}(\BF_\Lambda))}{(\lambda_{D,i} - \lambda_{D,j})^2} \bfgamma_j \bfgamma_i^T.
\end{eqnarray*}
